---
title: "ONA analysis for iPlan"
output: html_notebook
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
rm(list = ls())
library("rstudioapi")
setwd(dirname(getActiveDocumentContext()$path))
```

Uncomment and run this block if you haven't had these packages installed
```{r}
# install.packages("ona", repos = c("https://cran.qe-libs.org", "https://cran.rstudio.org"))
# install.packages("tma", repos = c("https://cran.qe-libs.org", "https://cran.rstudio.org"))
# install.packages("magrittr")
```

```{r include=FALSE, warning=FALSE}
library(ona)
library(tma)
library(magrittr)
library(rENA)
library(tidyverse)
library(readr)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(ggfortify)
library(data.table)
library(superheat)
library(rjson)
library(plotly)
library(RColorBrewer)
library(randomcoloR)
```

# 0. setting up constant variables (change as appropriate)
```{r}
mapid = "23917296"
wd = paste0(getwd(), "/data/")
```

# 0. read A B C matrices and other relevant data
```{r}
A_matrix = read_csv(paste0(wd, mapid, "_a_matrix.csv"))
B_matrix = read_csv(paste0(wd, mapid, "_b_matrix.csv"))
C_matrix = read.csv(paste0(wd, mapid, "_c_matrix.csv"))
sh_info = read.csv(paste0(wd, "LEM text - Stakeholders.csv"))
A = jsonlite::read_json(paste0(wd, mapid, ".json"))
reps = jsonlite::read_json(paste0(wd, mapid, "_reps.json"))
sub_result = readRDS(paste0(wd, mapid, "a_sub_result_new.rds")) #record satisfy level
```

```{r}
submission_name = C_matrix$user_name
submission_order = c()
sub_approval_count = c()
for (i in 1:length(sub_result)){
  submission_order = append(submission_order, sub_result[[i]]$userKey)
  sub_approval_count = append(sub_approval_count, sub_result[[i]]$approvalCount)
}
```

```{r}
sub_approval_count = sub_approval_count/9
# sub_approval_count
```

```{r}
sh_name = A_matrix %>%
  select(c(Name)) %>%
  unique() %>%
  pull()
```

```{r}
sh_info = sh_info %>% 
  filter(Name %in% sh_name) %>% 
  arrange(match(Name, sh_name)) %>% 
  unite("SHinfo", Name:Direction, remove = TRUE) %>% 
  pull()
```

reference:
luc_0 = "Commercial"
luc_1 = "Conservation"
luc_2 = "Cropland" 
luc_3 = "Industrial" 
luc_4 = "Limited Use"
luc_5 = "Pasture"
luc_6 = "Recreation"
luc_7 = "Residential HD" 
luc_8 = "Residential LD" 
luc_9 = "Timber" 
luc_10 = "Wetlands"

luc_vec = c("luc_0", "luc_1","luc_2","luc_3","luc_4","luc_5","luc_6","luc_7","luc_8","luc_9","luc_10")
luc_original = c("20", "31", "50", "21", "30", "60", "22", "23", "24", "40", "10")

# 1. combine conservation and limited use and set self-connection to zero
which means luc_1_X + luc_4_X, luc_X_1 + luc_X_4
```{r}
A_matrix_2 <- A_matrix
B_matrix_2 <- B_matrix
C_matrix_2 <- C_matrix
for (i in 1:11) {
  A_luc1x = which(names(A_matrix_2)==paste0("luc_", 1, "_", i-1))
  A_luc4x = which(names(A_matrix_2)==paste0("luc_", 4, "_", i-1))
  B_luc1x = which(names(B_matrix_2)==paste0("luc_", 1, "_", i-1))
  B_luc4x = which(names(B_matrix_2)==paste0("luc_", 4, "_", i-1))
  C_luc1x = which(names(C_matrix_2)==paste0("luc_", 1, "_", i-1))
  C_luc4x = which(names(C_matrix_2)==paste0("luc_", 4, "_", i-1))
  A_matrix_2[[A_luc1x]] <- A_matrix_2[[A_luc1x]] + A_matrix_2[[A_luc4x]]
  B_matrix_2[[B_luc1x]] <- B_matrix_2[[B_luc1x]] + B_matrix_2[[B_luc4x]]
  C_matrix_2[[C_luc1x]] <- C_matrix_2[[C_luc1x]] + C_matrix_2[[C_luc4x]]
}
for (i in 1:11) {
  A_lucx1 = which(names(A_matrix_2)==paste0("luc_", i-1, "_", 1))
  A_lucx4 = which(names(A_matrix_2)==paste0("luc_", i-1, "_", 4))
  B_lucx1 = which(names(B_matrix_2)==paste0("luc_", i-1, "_", 1))
  B_lucx4 = which(names(B_matrix_2)==paste0("luc_", i-1, "_", 4))
  C_lucx1 = which(names(C_matrix_2)==paste0("luc_", i-1, "_", 1))
  C_lucx4 = which(names(C_matrix_2)==paste0("luc_", i-1, "_", 4))
  A_matrix_2[[A_lucx1]] <- A_matrix_2[[A_lucx1]] + A_matrix_2[[A_lucx4]]
  B_matrix_2[[B_lucx1]] <- B_matrix_2[[B_lucx1]] + B_matrix_2[[B_lucx4]]
  C_matrix_2[[C_lucx1]] <- C_matrix_2[[C_lucx1]] + C_matrix_2[[C_lucx4]]
}
for (i in 1:11) {
  A_lucxx = which(names(A_matrix_2)==paste0("luc_", i-1, "_", i-1))
  B_lucxx = which(names(B_matrix_2)==paste0("luc_", i-1, "_", i-1))
  C_lucxx = which(names(C_matrix_2)==paste0("luc_", i-1, "_", i-1))
  A_matrix_2[[A_lucxx]] = 0
  B_matrix_2[[B_lucxx]] = 0
  C_matrix_2[[C_lucxx]] = 0
}

A_matrix_2 <- A_matrix_2 %>% select(-c(luc_4_0, luc_4_1, luc_4_2, luc_4_3, luc_4_4, 
                               luc_4_5, luc_4_6, luc_4_7, luc_4_8, luc_4_9, luc_4_10,
                               luc_0_4, luc_1_4, luc_2_4, luc_3_4, luc_4_4,
                               luc_5_4, luc_6_4, luc_7_4, luc_8_4, luc_9_4, luc_10_4))
B_matrix_2 <- B_matrix_2 %>% select(-c(luc_4_0, luc_4_1, luc_4_2, luc_4_3, luc_4_4, 
                               luc_4_5, luc_4_6, luc_4_7, luc_4_8, luc_4_9, luc_4_10,
                               luc_0_4, luc_1_4, luc_2_4, luc_3_4, luc_4_4,
                               luc_5_4, luc_6_4, luc_7_4, luc_8_4, luc_9_4, luc_10_4))
C_matrix_2 <- C_matrix_2 %>% select(-c(luc_4_0, luc_4_1, luc_4_2, luc_4_3, luc_4_4, 
                               luc_4_5, luc_4_6, luc_4_7, luc_4_8, luc_4_9, luc_4_10,
                               luc_0_4, luc_1_4, luc_2_4, luc_3_4, luc_4_4,
                               luc_5_4, luc_6_4, luc_7_4, luc_8_4, luc_9_4, luc_10_4))
```

# 2. make ABC col names consistent for the ease of later work
```{r}
colnames(A_matrix_2)[2] = "SH"
A_matrix_2 <- A_matrix_2 %>%
  select(-c(...1)) %>% 
  add_column(user_name = "NA", .before = "luc_0_0") %>%
  add_column(submission = "NA",.before = "luc_0_0") %>%
  add_column(index = 1:nrow(A_matrix), .before = "SH")
```

```{r}
colnames(B_matrix_2)[2] = "SH"
B_matrix_2 <- B_matrix_2 %>%
  select(-c(...1)) %>% 
  add_column(user_name = "NA", .before = "luc_0_0") %>%
  add_column(submission = "NA",.before = "luc_0_0") %>%
  add_column(index = 1:nrow(B_matrix), .before = "SH")
```

```{r}
C_matrix_2 <- C_matrix_2 %>%
  add_column(index = 1:nrow(C_matrix_2), .before = "user_name") %>%
  add_column(Name = "NA", .before = "user_name") %>%
  add_column(Satisfy = "NA",.before = "user_name") %>%
  add_column(N = "NA", .before = "user_name")
```

# 3.run ONA
call generate.ona.object function
```{r generate.ona.object}
generate.ona.object <- function(data, unit.col, meta.col, codes){
  output <- list()
  f.units <- unit.col
  ENA_UNIT <- rENA::merge_columns_c(f.units, cols = colnames(f.units));
  # ENA_UNIT <-  f.units
  f.raw <- data
  f.codes <- codes
  dena_data = directedENA:::ena.set.directed(f.raw, f.units, NA, f.codes)
  output.meta.data <- meta.col
  dena_data$meta.data <- data.table::as.data.table(cbind(ENA_UNIT, output.meta.data))
  for( i in colnames(dena_data$meta.data) ) {
    set(dena_data$meta.data, j = i, value = rENA::as.ena.metadata(dena_data$meta.data[[i]]))
  }
  code_length <- length(dena_data$rotation$codes);
  dena_data$rotation$adjacency.key <- data.table::data.table(matrix(c(
    rep(1:code_length, code_length),
    rep(1:code_length, each = code_length)),
    byrow = TRUE, nrow = 2
  ))
  directed.adjacency.vectors <- as.ena.matrix(data.table::as.data.table(data[, grep("V", colnames(data))]), "ena.connections")
  # aren't these two the same thing 
  dena_data$connection.counts <- data.table::as.data.table(cbind(dena_data$meta.data, directed.adjacency.vectors))
  dena_data$connection.counts = rENA::as.ena.matrix(x = dena_data$connection.counts, "ena.connections")
  for (i in which(!rENA::find_meta_cols(dena_data$connection.counts)))
    set(dena_data$connection.counts, j = i, value = as.ena.co.occurrence(as.double(dena_data$connection.counts[[i]])))
  dena_data$model$row.connection.counts = data.table::as.data.table(cbind(dena_data$meta.data, directed.adjacency.vectors))
  dena_data$model$row.connection.counts <- rENA::as.ena.matrix(dena_data$model$row.connection.counts, "row.connections")
  output = dena_data;
  return(output)
}
```

```{r}
# 1. prepare df

# df <- A_matrix
# df <- B_matrix
df <- C_matrix_2

names(df)[7:106] <- paste0("V",seq(1:100))
df$mapid = mapid

# 2. accum
accumC <- generate.ona.object(
  df,
  unit.col = df[,1:7],
  meta.col = df[,1:7],
  codes = as.vector(
    c("Commercial",
    "Conservation_lu",
    # "Conservation",
    "Cropland",
    "Industrial",
    # "Limited Use",
    "Pasture",
    "Recreation",
    "Residential HD",
    "Residential LD",
    "Timber",
    "Wetlands")))

# 3. model
setC <- model(accumC)

# 4. GoF
correlations(setC)

```

```{r}
# 1. prepare df

df1 <- A_matrix_2
# df <- B_matrix
# df <- C_matrix

names(df1)[7:106] <- paste0("V",seq(1:100))
df1$mapid = mapid

# 2. accum
accumA <- generate.ona.object(
  df1,
  unit.col = df1[,1:7],
  meta.col = df1[,1:7],
  codes = as.vector(
    c("Commercial",
    "Conservation_lu",
    # "Conservation",
    "Cropland",
    "Industrial",
    # "Limited Use",
    "Pasture",
    "Recreation",
    "Residential HD",
    "Residential LD",
    "Timber",
    "Wetlands")))

# 3. model
setA <- model(accumA)

# 4. GoF
correlations(setA)
```

# 4. project C points into A space
To do so, I need to make a set using C's accumulation and A's rotation matrix
```{r}
set=model(accumC, rotation.set = setA$rotation)
```

# 5. ona plotting 
## 5.1 setting global visual parameters here so that all ONA plots we generate are on the same scale
```{r}
node_size_multiplier = 0.2
node_position_multiplier = 1.0
edge_size_multiplier = 0.2
point_position_multiplier = 1.0
edge_arrow_saturation_multiplier = 1.0
```

```{r}
ona:::plot.ena.directed.set(setC) %>% 
  units( 
    points = setC$points,
    points_color = "black",
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE)
```

## 5.2 quick check points ARE being rotated
```{r}
ona:::plot.ena.directed.set(setA, title = "space used for projection and its points") %>%
  units(
    points = setA$points,
    points_color = "gray",
    show_mean = TRUE, show_points = TRUE, with_ci = FALSE) %>%
 nodes(
    node_size_multiplier = 0.001) 

ona:::plot.ena.directed.set(setC, title = "points need to be projected in its original space") %>%
  units( 
    points = setC$points,
    points_color = "black",
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE)%>%
 nodes(
    node_size_multiplier = 0.001) 

ona:::plot.ena.directed.set(set, title = "projected points in its new space") %>%
  units(
    points = set$points,
    points_color = "black",
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) %>%
  units(
    points = setA$points,
    points_color = "gray",
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) %>%
 nodes(
    node_size_multiplier = 0.001) 
```

## Cluster Check:


```{r}
ona:::plot.ena.directed.set(setA, title = "space used for projection and its points") %>%
  units(
    points = setA$points,
    points_color = "gray",
    show_mean = TRUE, show_points = TRUE, with_ci = FALSE) %>%
 nodes(
    node_size_multiplier = 0.001) 
```

```{r}
A = setA$points[ENA_DIRECTION== 'response']
```

## 5.3 YES 9 means + submission trajectory

```{r}
user_names <- unique(C_matrix$user_name)
n <- length(user_names)
colors_selected <- distinctColorPalette(n)
pie(rep(1,n), col=colors_selected)
```

```{r}
ona_plot <- function(includeSub = TRUE){
  colors <- c("green", "blue", "brown", "purple", "yellow", "deeppink", "Tan", "Cyan", "orange")

  p <- ona:::plot.ena.directed.set(set) %>%
    units(
      points = set$points,
      points_color = "white",
      point_position_multiplier = point_position_multiplier,
      show_mean = FALSE,
      show_points = TRUE,
      with_ci = FALSE
    )
  
  for (i in 1:length(sh_name)) {
    tryCatch({
      p <- p %>%
        units(
          points = setA$points[SH == sh_name[i] & Satisfy == "Yes"],
          points_color = colors[i],
          point_position_multiplier = point_position_multiplier,
          show_mean = TRUE,
          show_points = FALSE,
          with_ci = TRUE
        )
    }, error = function(e) {
      cat("An error occurred:", conditionMessage(e), "\n")
      # If an error occurs, set with_ci = FALSE
      p <- p %>%
        units(
          points = setA$points[SH == sh_name[i] & Satisfy == "Yes"],
          points_color = colors[i],
          point_position_multiplier = point_position_multiplier,
          show_mean = TRUE,
          show_points = FALSE,
          with_ci = FALSE
      )
    })
  }
  
  p <- p %>%
    nodes(
      node_size_multiplier = 0.01,
      node_position_multiplier = node_position_multiplier,
      self_connection_color = "blue")
  if(includeSub) {
    j = 0
    k = 1
    prev = ""
    for (i in 1:length(submission_name)) {
      if (submission_name[i] != prev) {
        j <- j+1
        prev <- submission_name[i]
        k <- 1
      }
      p <- p %>%
        add_annotations(
          x = set$points[ENA_DIRECTION == "response"]$SVD1[i],
          y = set$points[ENA_DIRECTION == "response"]$SVD2[i],
          text = paste0(substring(submission_name[i], 1, 2), "[", k, "]"),
          font = list(color = colors_selected[j]),
          showarrow = FALSE
        )
      k <- k+1
    }
  }
  p <- p %>%
  plotly::layout(showlegend = TRUE, legend = list(x = 100, y = 0.9)) %>% 
      style(name = "point", traces = c(2)) %>% 
    style(name = sh_info[1], traces = c(3)) %>% 
    style(name = sh_info[2], traces = c(4)) %>% 
    style(name = sh_info[3], traces = c(5)) %>% 
    style(name = sh_info[4], traces = c(6)) %>% 
    style(name = sh_info[5], traces = c(7)) %>% 
    style(name = sh_info[6], traces = c(8)) %>% 
    style(name = sh_info[7], traces = c(9)) %>% 
    style(name = sh_info[8], traces = c(10)) %>% 
    style(name = sh_info[9], traces = c(11))
  return(p)
}

```

```{r}
ona_plot(FALSE)
ona_plot()
```

